A comparative analysis of AquaMaps and IUCN species distribution maps

### 2015-12-14 ms_outline.Rmd
added iucn level plot
what changes did I make here?  nooo!!!

___Total species occurrences for each data set: all AM, all IUCN, and overlap (one? the other? occurrences of both?)___

![](figures/all_aquamaps_map.png)

@@

AquaMaps and IUCN marine species distribution maps ostensibly describe the same information, and while differences in methodology and input data will inevitably lead to differences, we would expect to see strong similarities between range maps for any given species.

>>>>

___N Species by cell for each data set: all AM, all IUCN, and overlap (one? the other? occurrences of both?)___

![](figures/all_aquamaps_map.png)
![](figures/all_iucn_map.png)

___Note that these level plots show the mean() of the cell value for each row and each column.___  For a difference plot, maybe there's another function that can show us that?

@@

AquaMaps and IUCN marine species distribution maps ostensibly describe the same information, and while differences in methodology and input data will inevitably lead to variation between range maps for any given species, we would expect to see some spatial correlation.
